A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2022-01-19 analysis/paper/paper.Rmd
Exponential distance to shoreline

```{r distances}
distances2 <- distances %>%
  filter(year <= -2500 & rcarb_cor == "t" & type == "forager") %>% 
  mutate(hordist = ifelse(str_detect(sitename, "Løvås"), 0, hordist),
         topodist = ifelse(str_detect(sitename, "Løvås"), 0, topodist),
         vertdist = ifelse(str_detect(sitename, "Løvås"), 0, vertdist))

distances3 <- distances %>%
  filter(year <= -4000 & rcarb_cor == "t" & type == "forager") %>% 
  mutate(hordist = ifelse(str_detect(sitename, "Løvås"), 0, hordist),
         topodist = ifelse(str_detect(sitename, "Løvås"), 0, topodist),
         vertdist = ifelse(str_detect(sitename, "Løvås"), 0, vertdist))
```
# Results

>>>>

```{r distances}
distances2 <- distances %>%
  filter(year <= -2500 & rcarb_cor == "t" & type == "forager") %>% 
  mutate(hordist = ifelse(hordist < 0, 0, hordist),
         topodist = ifelse(topodist < 0, 0, topodist),
         vertdist = ifelse(vertdist < 0, 0, vertdist))

distances3 <- distances %>%
  filter(year <= -4000 & rcarb_cor == "t" & type == "forager") %>% 
  mutate(hordist = ifelse(hordist < 0, 0, hordist),
         topodist = ifelse(topodist < 0, 0, topodist),
         vertdist = ifelse(vertdist < 0, 0, vertdist))
```
# Results
